### 2014-09-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to report

While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor. In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure. The following lines define the gypsum material in the FDS input file:

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh. The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

@@

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                 &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                           &  9~min                                        &  --                                \\
Grid Cell Size                            &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                   &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                          &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                          &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                          &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fires}           \\
                                          &  Basement flashover fire: 15~MW               &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}  &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                          &  $\rho$: 810~kg/m$^3$                         &                                    \\
                                          &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}              &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

>>>>

While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor. In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure. The following lines define the gypsum material and surface in the FDS input file:

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.

@@

The domain was divided into 16 meshes (each containing between 272,000 and 367,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                    &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                              &  9~min                                        &  --                                \\
Grid Cell Size                               &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
                                             &  Basement flashover fire: 14~MW               &                                    \\
                                             &  Basement balcony fire: 1~MW                  &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}     &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                             &  $\rho$: 810~kg/m$^3$                         &                                    \\
                                             &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}              &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}
